\documentclass[helvetica,openbib,totpages]{europecv}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage[a4paper,top=1.27cm,left=1cm,right=1cm,bottom=2cm]{geometry}
\usepackage[english]{babel}
\usepackage{bibentry}
\usepackage{url}

\renewcommand{\ttdefault}{phv} % Uses Helvetica instead of fixed width font

\ecvname{Ognibene, Luca}
\ecvfootername{Luca Ognibene}
\ecvaddress{25, largo Sandro Pertini, 26041, Casalmaggiore, Italy}
\ecvtelephone[]{3347378858}
%\ecvfax{(Remove if not relevant)}
\ecvemail{\url{luca.ognibene@gmail.com}} 
\ecvnationality{Italian}
\ecvdateofbirth{28/08/1981}
\ecvgender{Male}
%\ecvpicture[width=2cm]{mypicture}
\ecvfootnote{For more information go to \url{http://europass.cedefop.eu.int}\\
\textcopyright~European Communities, 2003.}

\begin{document}
\selectlanguage{english}


\begin{europecv}
\ecvpersonalinfo[5pt]
%\ecvitem{\large\textbf{Desired employment/ Occupational~field}}{\large\textbf{(Remove if not relevant)}}

\ecvsection{Work experience}
\ecvitem{Dates}{2004-}
\ecvitem{Occupation or position held}{Project manager, Developer}
\ecvitem{Main activities and responsibilities}{My main task is software design and development in
  C/Python/LUA but i also help to management our IT infrastructure (we're a small firm).
  I work on both server and client development: the server is a collection of applications written
  in Python/C/GStreamer/Twisted and the client is a cross-platform (Windows, Linux) cross-browser (Internet Explorer, 
  Firefox) plugin written in C/Clutter/GStreamer used to show live or recorded streams from the
  server.
  I also work on integrating
  external hardware components like rfid devices(wec, eurochip), automation bus (modbus,
  vimar, myhome bticino, echobus, securlan..) or network camera from Axis, Panasonic, ACTi..)
  in our system. I worked on some image analysis projects like plate recognition or motion detection.
}
\ecvitem{Name and address of employer}{Anteklab srl, Via Verdi
  n.9, 46047 Porto Mantovano (MN)}
\ecvitem{Type of business or sector}{Videosecurity}

\ecvitem{Date}{2003}
\ecvitem{Occupation or position held}{Stage}
\ecvitem{Main activities and responsibilities}{
Development of a document handling project in Visual Basic}
\ecvitem{Name and address of employer}{Via dei Mercati 7 –
  43100 Parma}
\ecvitem{Type of business or sector}{Information Technology Services}


\ecvsection{Education and training}

\ecvitem{Dates}{2000-2004}
\ecvitem{Title of qualification awarded}{Academic Degree}
\ecvitem{Name and type of organization providing education and
  training}{Universita' degli studi di Parma}


\ecvsection{Personal skills and~competences}

\ecvmothertongue[5pt]{Italian}
\ecvitem{\large Other language(s)}{English}
\ecvlanguageheader{(*)}
\ecvlastlanguage{English}{\ecvCOne}{\ecvCOne}{\ecvBTwo}{\ecvBTwo}{\ecvCOne}
\ecvlanguagefooter[10pt]{(*)}


\ecvitem[10pt]{\large Organisational skills and competences}{Good experience
  in teamwork after years of work in some open source projects (Xine,
  GStreamer, GAI, Maemo and others)}
%\ecvitem[10pt]{\large }{Replace this text by a description of these competences and indicate where they were acquired (remove if not relevant).}
%\ecvitem[10pt]{\large Technical skills and competences}{Replace this text by a description of these competences and indicate where they were acquired (remove if not relevant).}
\ecvitem[10pt]{\large Computer skills and competences}{
\begin{description}
\item Programming languages: C,Python,LUA,SQL. Right now i prefer to develop in Python and use C only when performance really matters
\item Database: I've used MySQL, PostgreSQL and Microsoft SQL Server
\item Markup: XML, HTML, YAML, JSON
\item Presentation: Latex (or LyX)
\item Operating systems: Linux, Microsoft Windows
\item Network protocols: i've worked with HTTP, RTP/RTSP/RTCP, XMLRPC, SMTP, FTP, XMPP
\item Applications: GIMP, Suite OpenOffice, Suite Microsoft Office,
  Blender, Inkscape, Emacs, GNOME desktop
\item IT Infrastructure: BugZilla, Trac, Subversion, GIT, Bzr, Various
  backup tools
\item Frameworks: GObject, GStreamer, Twisted, Clutter, Firefox
\item GStreamer: i know how to use GStreamer in C or Python applications and i know how to develop simple or more complicated plugins
  like sources, filters, sinks, i've never written any (de)muxers plugins. I also contributed some patches and reported bugs at b.g.o 
  (luca.ognibene@gmail.com or ``luogni'' or ``skaboy''). I also had cvs (long time ago..) write access to gst-ffmpeg 0.8 while i was
  working on it.
\item Twisted: I work with twisted so i can use a simple async interface in my python programs but i'm not really a Twisted guru.
\item Clutter: I use clutter and gst-clutter to show live or on-demand streams in a cross-platform and fast way.
\item Firefox/IE: i know how to do firefox/IE plugins and extensions.
\item Optimization: i enjoy fixing bottlenecks and performance bugs in applications.. but only when it's needed!
\end{description}

}
%\ecvitem[10pt]{\large Artistic skills and competences}{Replace this text by a description of these competences and indicate where they were acquired (remove if not relevant).}
%\ecvitem[10pt]{\large Other skills and competences}{Replace this text by a description of these competences and indicate where they were acquired (remove if not relevant).}
\ecvitem{\large Driving licence(s)}{B}

%\ecvsection{Additional information}
%\ecvitem[10pt]{}{Include here any other information that may be relevant, for example contact persons, references, etc. (Remove heading if not relevant).}
%\bibliographystyle{plain}
%\nobibliography{publications}
%\ecvitem{}{\textbf{Publications}}
%\ecvitem{}{\bibentry{pub1}}
%\ecvitem[10pt]{}{\bibentry{pub2}}
%\ecvitem{}{\textbf{Personal interests}}
%\ecvitem{}{\ldots}

%\ecvsection{Annexes}
%\ecvitem{}{List any item attached to the CV}
\end{europecv}


\end{document} 
